A molecular dynamics study of the solvation of carbon dioxide in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}

### 2018-09-02 ionic_liquids.tex
Figures can be converted to pdf to save compilation time
Elimination of some packages for faster compilation
Changes in the abstract

%\documentclass[3p,preprint]{elsarticle}
\documentclass[3p,twocolumn]{elsarticle}
\usepackage[colorlinks,citecolor=blue]{hyperref}
\usepackage{lineno}
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{commath}
\usepackage{amssymb}
%\usepackage{scalerel}
\usepackage{natbib}
\usepackage[version=4]{mhchem}

@@

\usepackage{amsmath}
\usepackage{commath}
\usepackage{graphicx,bm}
\usepackage{epstopdf}
\usepackage{float}
\biboptions{sort&compress}
\modulolinenumbers[5]
\usepackage{subfig}

\usepackage[T1]{fontenc}
\usepackage{xr}
\externaldocument{supp_material}

\journal{Journal of \LaTeX\ Templates}

%%%%%%%%%%%%%%%%%%%%%%%
%% Elsevier bibliography styles
%%%%%%%%%%%%%%%%%%%%%%%
%% To change the style, put a % in front of the second line of the current style and
%% remove the % from the second line of the style you would like to use.
%%%%%%%%%%%%%%%%%%%%%%%
%% Numbered
%\bibliographystyle{model1-num-names}

%% Numbered without titles
%\bibliographystyle{model1a-num-names}

%% Harvard
%\bibliographystyle{model2-names.bst}\biboptions{authoryear}

%% Vancouver numbered
%\usepackage{numcompress}\bibliographystyle{model3-num-names}

%% Vancouver name/year
%\usepackage{numcompress}\bibliographystyle{model4-names}\biboptions{authoryear}

%% APA style
%\bibliographystyle{model5-names}\biboptions{authoryear}

%% AMA style
%\usepackage{numcompress}\bibliographystyle{model6-num-names}

%% `Elsevier LaTeX' style
\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{A molecular dynamics study of the solvation of \ce{CO_2}, water, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}

@@

\begin{abstract}
In this paper, we calculate solvation free energies in ionic liquids and predict macroscopic properties required in the design of chemical processes.
Carbon dioxide from combustion processes is one of the main sources of anthropogenic generation of greenhouse gases.
On the other hand, the potential of \ce{[emim][B(CN)_4]} for its capture has recently been reported.
For comparison, the solvents \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are analyzed, both at infinite dilution and at high concentrations of \ce{CO_2}.
Our results confirm what is experimentally observed, namely a considerably lower pressure is required to dissolve a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]}.
The infinite-dilution activity coefficients of hexane, benzene, cyclohexane, ethanol, and water in \ce{[emim][B(CN)_4]} are also calculated, and a comparison is made with experimental values recently reported in literature.
\end{abstract}

@@

\begin{figure*}
\centering
\subfloat[Koller~\textit{et al.}~\cite{Koller_2012}]{%
  \includegraphics[width=.4\linewidth]{koller.png}}%
\subfloat[Batista~\textit{et al.}~\cite{Batista_2015}]{%  
  \includegraphics[width=.4\linewidth]{batista.png}}%

\subfloat[Liu~\textit{et al.}~\cite{Liu_2014}]{%
  \includegraphics[width=.4\linewidth]{Liu.png}}%
\subfloat[Weber and Kirchner~\cite{Weber_2016}]{%
  \includegraphics[width=.4\linewidth]{Weber.png}}%
\caption{Combined distribution function of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs for each model of \ce{[emim][B(CN)_4]}.}
\label{fig:dihedrals_emim}
\end{figure*}

@@

\begin{figure}[ht]
\centering
  \includegraphics[width=\linewidth]{Ludwig.png}%

  \includegraphics[width=\linewidth]{Ludwig_anion.png}%
\caption{Combined distribution function of (a) the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, and (b) of the dihedral angles of the contiguous  C1-S1-N1-S2 and S1-N1-S2-C2 chains, obtained from NPT-MD simulations of 250 molecules of \ce{[emim][NTf_2]}.}
\label{fig:die_ntf2}
\end{figure}

>>>>

%\documentclass[3p,preprint]{elsarticle}
\documentclass[3p,twocolumn]{elsarticle}

\usepackage[colorlinks,citecolor=blue]{hyperref}
\usepackage{lineno}
\modulolinenumbers[5]
\usepackage{amsmath}
\usepackage{ifthen}
\usepackage{commath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage[version=4]{mhchem}

@@

\usepackage{amsmath}
\usepackage{commath}
\usepackage{graphicx}
\DeclareGraphicsExtensions{.pdf,.eps,.png}
\usepackage{float}
\usepackage{subfig}

\journal{Fluid Phase Equilibria}

\bibliographystyle{elsarticle-num}
%%%%%%%%%%%%%%%%%%%%%%%

@@

\title{A molecular dynamics study of the solvation of carbon dioxide in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}
%\title{A molecular dynamics study of the solvation of \ce{CO_2}, \ce{H_2O}, and some organic compounds in the ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]}}

@@

\begin{abstract}
In this paper, we calculate solvation free energies of several compounds in ionic liquids.
These free energies are used to compute properties such as Henry's law constants and activity coefficients, generally required to the design of environmentally sustainable processes.
It is known, for instance, that carbon dioxide from combustion is one of the main sources of anthropogenic greenhouse gases.
Recently, the propensity of ionic liquid \ce{[emim][B(CN)_4]} for the physisorption of \ce{CO_2} has been reported, which makes it a potential solvent for carbon capture.
In the present work, molecular dynamics simulations of the solvation of \ce{CO_2} in ionic liquids \ce{[emim][B(CN)_4]} and \ce{[emim][NTf_2]} are carried out both at infinite dilution and at high concentrations.
A systematic study is performed by comparing several force fields and assessing the efficacy of simplification measures such as rigid-body dynamics and pairwise electrostatics.
Our results confirm recent experimental observations that, for a given volume of solvent, lower pressure is required to absorb a certain amount of \ce{CO_2} in \ce{[emim][B(CN)_4]} than in other ionic liquids.
\end{abstract}

@@

\begin{figure*}
\centering
\subfloat[Koller~\textit{et al.}~\cite{Koller_2012}]{%
  \includegraphics[width=.4\linewidth]{koller}}%
\subfloat[Batista~\textit{et al.}~\cite{Batista_2015}]{%  
  \includegraphics[width=.4\linewidth]{batista}}%

\subfloat[Liu~\textit{et al.}~\cite{Liu_2014}]{%
  \includegraphics[width=.4\linewidth]{Liu}}%
\subfloat[Weber and Kirchner~\cite{Weber_2016}]{%
  \includegraphics[width=.4\linewidth]{Weber}}%
\caption{Combined distribution function of the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, as sampled in NPT-MD simulations of 250 ion pairs for each model of \ce{[emim][B(CN)_4]}.}
\label{fig:dihedrals_emim}
\end{figure*}

@@

\begin{figure}[ht]
\centering
  \includegraphics[width=\linewidth]{Ludwig}%

  \includegraphics[width=\linewidth]{Ludwig_anion}%
\caption{Combined distribution function of (a) the dihedral angles of C1-N2-C5-C6 and C2-N2-C5-C6, and (b) of the dihedral angles of the contiguous  C1-S1-N1-S2 and S1-N1-S2-C2 chains, obtained from NPT-MD simulations of 250 molecules of \ce{[emim][NTf_2]}.}
\label{fig:die_ntf2}
\end{figure}
